Crystal as a thermodynamic computer

### 2024-09-16 paper/main.tex
update

    % Text Node
    \draw (379,111.8) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \cdots $};
    % Text Node
    \draw (379,141.8) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \cdots $};
    % Text Node
    \draw (379,172.09) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \cdots $};
    % Text Node
    \draw (379,241.8) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \cdots $};
    % Text Node
    \draw (283,193.97) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \vdots $};
    % Text Node
    \draw (322.5,193.97) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \vdots $};
    % Text Node
    \draw (363,193.97) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \vdots $};
    % Text Node
    \draw (420.1,194) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \vdots $};
    % Text Node
    \draw (382.4,194.52) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \ddots $};
    % Text Node
    \draw (292,45) node [anchor=north west][inner sep=0.75pt]   [align=left] {${Heat\ Zone}$};
    % Text Node
    \draw (494.80,152.01) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\scriptsize {$p$}}};
    % Text Node
    \draw (478.75,176.45) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\scriptsize {$q$}}};
    % Text Node
    \draw (495.60,201.80) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\scriptsize {$r$}}};
    % Text Node
    \draw (539.00,174.95) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\scriptsize {$q'$}}};
    % Text Node
    \draw (510.60,175.95) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\scriptsize {$A$}}};

@@

Assume the SA procedure in each block has an error probability $\epsilon$.
Repeating the procedure in $\frac{M}{W}$ blocks results in a success probability of $(1 - \epsilon)^{\frac{M}{W}}$ for finding the global ground state. 
To fix the success probability for arbitrary $M$, we must have $\epsilon \sim \frac{W}{M}$.
The annealing time $t_{th}$ required to achieve a certain error in each block is determined by the spectral gap $\Delta$ of the Markov transition matrix of the SA update on the block.
%Since the largest eigenvalue of a transition matrix is 1, the spectral gap is $\Delta = 1 - \lambda_2$, where $\lambda_2$ is the second-largest eigenvalue.
The scaling behavior of $\Delta$ and block size $W$ can be complicated, in the worst case, it can be exponential, i.e.,
\begin{equation}
    \label{eq:spectral-gap}
    \Delta \sim e^{-W}.
\end{equation}
Consequently, $t_{th}$ is related to $\epsilon$ by $\left( 1-\Delta \right) ^ {t_{th}} = \epsilon$, which gives $t_{th} \sim \ln\left(\frac{M}{W}\right)e^{W}$, and the total sweep times scale as:
\begin{equation}\label{eq:totaltime}
t_{\rm total} \sim \frac{M}{W}\ln\left(\frac{M}{W}\right)e^W.
\end{equation}

@@

We can define an effective heat zone with width $W'$ as the width of the raising edge of the temperature distribution, where the spins can be cooled actively.
%Defining $\Delta E_{max}$ to be the largest possible energy change when a spin is fliped.
%The effective heat zone with width $W'(\Lambda)$ should then be $[y-W'(\Lambda), y]$, where position $y$ satisfying 
%$\exp(\frac{\Delta E_{max}}{T(y)}) = 0.1$ and $y<L(t)$. 
% Since the layers in fronts of the effective heat zone can only be fliped with a $\epsilon$ probability if the local energy would increase. 
The spins outside the effective heat zone are either frozen (too cold) or flip randomly (too hot).
As a spin flips with a probability $\sim e^{-\Delta E/T}$, the cold edge of the heat zone can be defined as the position where the probability of flipping is $\epsilon$.
We have $W'$ scales with the required error probability $\epsilon$ as:
\begin{equation}
    e^{-\frac{\Delta E}{T_{\rm max}}\Lambda^{cW'}} \sim \epsilon
\end{equation}
where $c$ is an empirical constant and can be determined during the experiment. 
\jinguo{How about this?}
\ym{But I still don't think the constant $c$ is reasonable in this version. Anyway it is a better 
description for $W'$.}

We can further derive $e^{W'}$ as function of $\Lambda$:
\begin{equation}
    e^{\ln(\Lambda)cW'}\sim \ln(\frac{1}{\epsilon})\rightarrow e^{W'}\sim \ln(\frac{1}{\epsilon})^{\frac{1}{c\ln(\Lambda)}}
\end{equation}

Combining with \Cref{eq:totaltime} and $\epsilon \sim \frac{W'}{M}$, the total annealing time can be estimated as
\begin{equation}
    \label{eq:total-annealing-time}
    t_{\rm total} \sim \frac{M}{W'}\left(\ln\left(\frac{M}{W'}\right)\right)^{1+ \frac{1}{c\ln(\Lambda)}}
\end{equation}

To determine the relationship between the total annealing time and the input size $N$, we should
further discuss the relationship between the spectral gap given in  \Cref{eq:spectral-gap} and inputs size $N$.
However, we failed to find a direct relationship.
Numerical result shows that computing complexity is linear to $N$. Thus a total sweep time
for the computation should scale as $NM\log^{1 + \frac{1}{c\ln(\Lambda)}}(M)$.
\ym{Please help me to think about how to evaluate the time complexity while $N$ increases.}\jinguo{Leave it to Maddie}
The moving speed $v$ can be then calculated as

\begin{equation}
    \label{eq:moving-speed}
    v \propto \frac{t_{total}}{M} = N\log^{1 + \frac{1}{c\ln(\Lambda)}}(M)
\end{equation}

>>>>

    % Text Node
    \draw (379,111.8) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \cdots $};
    % Text Node
    \draw (379,141.8) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \cdots $};
    % Text Node
    \draw (379,172.09) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \cdots $};
    % Text Node
    \draw (379,241.8) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \cdots $};
    % Text Node
    \draw (283,193.97) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \vdots $};
    % Text Node
    \draw (322.5,193.97) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \vdots $};
    % Text Node
    \draw (363,193.97) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \vdots $};
    % Text Node
    \draw (420.1,194) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \vdots $};
    % Text Node
    \draw (382.4,194.52) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \ddots $};
    % Text Node
    \draw (292,45) node [anchor=north west][inner sep=0.75pt]   [align=left] {${Heat\ Zone}$};
    % Text Node
    \draw (494.80,152.01) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\scriptsize {$p$}}};
    % Text Node
    \draw (478.75,176.45) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\scriptsize {$q$}}};
    % Text Node
    \draw (495.30,201.60) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\footnotesize {$r$}}};
    % Text Node
    \draw (539.00,174.95) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\scriptsize {$q'$}}};
    % Text Node
    \draw (510.60,175.95) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\scriptsize {$A$}}};

@@

Assume the SA procedure in each block has an error probability $\epsilon$.
Repeating the procedure in $\frac{M}{W}$ blocks results in a success probability of $(1 - \epsilon)^{\frac{M}{W}}$ for finding the global ground state. 
To fix the success probability for arbitrary $M$, we must have $\epsilon \sim \frac{W}{M}$.
The annealing time $t_{th}$ required to achieve a certain error in each block is determined by the spectral gap $\Delta$ of the Markov transition matrix of the SA update on the block.
%Since the largest eigenvalue of a transition matrix is 1, the spectral gap is $\Delta = 1 - \lambda_2$, where $\lambda_2$ is the second-largest eigenvalue.
The scaling behavior of $\Delta$ and block size $W$ can be complicated, in the worst case, it can be exponential, i.e.,
\begin{equation}
    \label{eq:spectral-gap}
    \Delta \sim e^{-f(W)},
\end{equation}
where $f(W)$ is a polynomial of $W$. Consequently, $t_{th}$ is related to $\epsilon$ by $\left( 1-\Delta \right) ^ {t_{th}} = \epsilon$, which gives $t_{th} \sim \ln\left(\frac{M}{W}\right)e^{f(W)}$, and the total sweep times scale as:
\begin{equation}\label{eq:totaltime}
t_{\rm total} \sim \frac{M}{W}\ln\left(\frac{M}{W}\right)e^{f(W)}.
\end{equation}

@@

We can define an effective heat zone with width $W'$ as the width of the raising edge of the temperature distribution, where the spins can be cooled actively.
%Defining $\Delta E_{max}$ to be the largest possible energy change when a spin is fliped.
%The effective heat zone with width $W'(\Lambda)$ should then be $[y-W'(\Lambda), y]$, where position $y$ satisfying 
%$\exp(\frac{\Delta E_{max}}{T(y)}) = 0.1$ and $y<L(t)$. 
% Since the layers in fronts of the effective heat zone can only be fliped with a $\epsilon$ probability if the local energy would increase. 
The spins outside the effective heat zone are either frozen (too cold) or flip randomly (too hot).
As a spin flips with a probability $\sim e^{-\Delta E/T}$, the cold edge of the heat zone can be defined as the position where the probability of flipping is $\epsilon$.
We have $W'$ scales with the required error probability $\epsilon$ as:
\begin{equation}
    e^{-\frac{\Delta E}{T_{\rm max}}\Lambda^{W'}} \sim \epsilon
\end{equation}
\ym{But I still don't think the constant $c$ is reasonable in this version. Anyway it is a better 
description for $W'$.}
\jinguo{I changed $c$ to $1/c$}

We can further derive $e^{W'}$ as function of $\Lambda$ by taking the logarithm of both sides:
\begin{equation}
    e^{\ln(\Lambda)W'}\sim \ln(\epsilon^{-1})\rightarrow e^{W'}\sim \ln(\epsilon^{-1})^{\frac{1}{\ln(\Lambda)}}
\end{equation}

Let $f(x) = c x + b$, then $e^{f(W')} \sim \ln(\epsilon^{-1})^{\frac{c}{\ln(\Lambda)}}$.
Combining with \Cref{eq:totaltime} and the requirement of $\epsilon \sim \frac{W'}{M}$, the total annealing time can be estimated as
\begin{equation}
    \label{eq:total-annealing-time}
    t_{\rm total} \sim \frac{M}{W'}\ln\left(\frac{M}{W'}\right)^{1+ \frac{c}{\ln(\Lambda)}}
\end{equation}
The reason why we choose $f$ to be linear is due to the simplicity of the model, and it turns out to be a good approximation in the numerical simulation.
%To determine the relationship between the total annealing time and the input size $N$, we should
%further discuss the relationship between the spectral gap given in  \Cref{eq:spectral-gap} and inputs size $N$.
%However, we failed to find a direct relationship.
%Numerical result shows that computing complexity is linear to $N$.
%Thus a total sweep time for the computation should scale as $NM\log^{1 + \frac{c}{\ln(\Lambda)}}(M)$.
\ym{Please help me to think about how to evaluate the time complexity while $N$ increases.}\jinguo{Leave it to Maddie}
The computing speed $v$ defined as operations per unit time, can be estimated as
\begin{equation}
    \label{eq:moving-speed}
    v = \frac{M}{t_{total}} \sim \ln(M)^{-(1 + \frac{c}{\ln(\Lambda)})}
\end{equation}
As the computational step $M$ increases, the computing speed $v$ decreases logarithmically.
